---
title: "Mechanisms for Teacher-like-me Paper"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: ["dcolumn", "booktabs", "caption", "float"]
    toc: yes
    toc_depth: 4
    keep_tex: yes
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(haven, estimatr, extrafont, texreg, janitor, hrbrthemes, xtable, papeR, tidyverse, compareGroups)

extrafont::loadfonts()
```

```{r}
# Data
df_stu <- 
  read_dta(here::here("data", "stu_admin_all_latest.dta")) %>%
  mutate(
    reservation = dplyr::recode(reservation, "Non-reservation" = 0L, "Reservation" = 1L, .default = NA_integer_)
  )


df <- 
  read_dta(here::here("data", "all_appended.dta")) %>% 
  distinct(stdid, course_name, facid, .keep_all = T) %>% 
  left_join(
    df_stu %>% 
      select(stdid, classid, department_id, reservation, ea_stud_group_criteria, grade),
    by = "stdid"
  ) %>%
  filter(ea_stud_group_criteria == 2, grade == 2) %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid")


# fixing for course cleaning done by sk in sep 2021
df <-
  df %>% 
  left_join(
    read_dta(here::here("data/students_clean.dta")),
    by = c("department_id", "course_name")
  ) %>% 
  mutate(
    course_name = if_else(!is.na(course_clean_sk), course_clean_sk, course_name)
  ) %>%
  distinct(stdid, course_name, facid, .keep_all = T)


# grade data after veda's work
df_grades <-
  read_dta(here::here("data/30jan2022/df_gradefac.dta")) %>% 
  filter(facid != "") %>%
  left_join(df_stu %>% select(stdid, department_id, reservation, b_i_jeemain_score, b_math_g1_score, b_physics_g1_score, elite), by = "stdid") %>%
  left_join(read_dta("data/controls.dta"), by = "stdid") %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid") %>% 
  arrange(department_id, course_name, course_grade_clean) %>% 
  group_by(department_id, course_name) %>% 
  mutate(
    course_rank = (scale(course_grade_clean) %>% pnorm() * 100) %>% as.vector
  ) %>% 
  ungroup() %>% 
  mutate(
    father_college = if_else(father_ed_ind > 3 & !is.na(father_ed_ind), 1L, 0L),
    father_college = if_else(is.na(father_ed_ind), NA_integer_, father_college),
    mother_college = if_else(mother_ed_ind > 3 & !is.na(mother_ed_ind), 1L, 0L),
    mother_college = if_else(is.na(mother_ed_ind), NA_integer_, mother_college),
    ses = ses %>% as.integer(),
  ) %>%
  relocate(department_id, course_name, stdid, course_rank) %>% 
  rename(reservation_stu = reservation, fac_teaching = fac_tpi_score7_z)

# df_grades %>% drop_na() %>% glimpse()
# df_grades %>% select(contains("college"))

df_mechanism <-
  df_grades %>%
  select(facid, reservation_fac, department_id, course_name, stdid) %>% 
  left_join(
    read_dta(here::here("data/fac_covars1.dta")) %>% 
      mutate_at(
        vars(starts_with("tpi_")),
        ~ scale(.) %>% as.vector
      ), 
    by = "facid"
  ) %>% 
  left_join(read_dta(here::here("data/fac_covars3.dta")), by = "facid") %>% 
  left_join(read_dta(here::here("data/fac_covars2.dta")), by = "facid") %>% 
  mutate_at(vars(starts_with("weekly")), ~ parse_number(.))

rm(df, df_stu, df_grades)
```

\newpage


## TPI Scores

Model:

$TPI_{c} = \alpha + \beta_2RT_c + \gamma_2T_c + \lambda_{course} + \lambda_i + \epsilon_{ic}$ 


The TPI scores used are standardized (mean 0, sd 1 across all surveyed faculty). The model includes course and student fixed effects. Standard errors are clustered at faculty level.


```{r, results='asis'}
lm_tpi1 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score1 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi2 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score2 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi3 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score3 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi4 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score4 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi5 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score5 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi6 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score6 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi7 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score7 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi8 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score8 ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_tpi_total <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(tpi_score_total ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)


knitreg(list(lm_tpi1, lm_tpi2, lm_tpi3, lm_tpi4, lm_tpi5, lm_tpi6, lm_tpi7, lm_tpi8, lm_tpi_total), custom.note = "%stars \n Standard errors clustered at faculty level.", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 2, custom.model.names = c("Course info provided", "Supporting info provided", "In-class features and activities", "Assignments", "Feedback and testing", "Other", "Train/guide TAs", "Collaboration", "Total"))

#texreg(list(lm_tpi3, lm_tpi5, lm_tpi8, lm_tpi_total), custom.note = "%stars \n Standard errors clustered at faculty level.", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 2, custom.model.names = c("In-class features and activities", "Feedback and testing", "Collaboration", "Total"))
```

\newpage

## Hours spent

Model:

$weeklyHours_{c} = \alpha + \beta_2RT_c + \gamma_2T_c + \lambda_{course} + \lambda_i + \epsilon_{ic}$ 


The weekly hours used are absolute values (not standardized). The model includes course and student fixed effects. Standard errors are clustered at faculty level.


```{r, results='asis'}
lm_hours1 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_administrative ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours2 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_advising_students ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours3 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_course ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours4 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_homework_tests ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours5 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_improving_teaching ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours6 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_lessons_planning ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours7 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_part_time_job ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours8 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_research ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours9 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_teaching_class ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours10 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_teaching_related ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)

lm_hours11 <-
  df_mechanism %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(weekly_hours_tutoring ~ reservation_fac + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_female, data = ., fixed_effects = ~ stdid + fe_var, se_type = "stata", clusters = facid)


knitreg(list(lm_hours1, lm_hours2, lm_hours3, lm_hours4, lm_hours5, lm_hours6, lm_hours7, lm_hours8, lm_hours9, lm_hours10, lm_hours11), custom.note = "%stars \n Standard errors clustered at faculty level.", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 2, custom.model.names = c("Administrative", "Advising students", "Course related work", "Homework/tests", "Improving teaching", "Lesson planning", "Part-time job", "Research", "Teaching class", "Teaching related", "Tutoring"))


texreg(list(lm_hours1, lm_hours2, lm_hours6, lm_hours7, lm_hours8, lm_hours9), custom.note = "%stars \n Standard errors clustered at faculty level.", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 2, custom.model.names = c("Administrative", "Advising students", "Lesson planning", "Part-time job", "Research", "Teaching class"))
```


















