---
title: "Comparing Models 2 and 3 for Gender Paper"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: ["dcolumn", "booktabs", "caption", "float"]
    toc: yes
    toc_depth: 6
    keep_tex: yes
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(haven, estimatr, extrafont, texreg, janitor, hrbrthemes, xtable, papeR, tidyverse, compareGroups, Hmisc, skimr)
```


# Defining models

- Model 1: student female, faculty female, student female x faculty female interaction, course fixed effects (level of randomization)
- Model 2: add student controls and faculty controls to Model 1
- Model 3: add student fixed effects to Model 2 (student controls drop out)
- Model 4: add faculty fixed effects to Model 3 (faculty controls drop out)
- Model 5: add classroom fixed effects to Model 4 (faculty fixed effects should drop out)

We start with 1881 unique students in our data from 11 colleges. For all models, we exclude 86 students who face no variation in instructor gender across all courses they have taken in the first two years of college. As a result, all models represent a sample of 1795 students.

\newpage

# Main Tables

```{r}
# Student Data
df_stu <- 
  read_dta(here::here("data", "stu_admin_all_latest.dta")) %>%
  left_join(read_dta(here::here("data/reservation_new.dta")), by = "stdid") %>% 
  mutate(
    reservation = dplyr::recode(reservation, "Non-reservation" = 0L, "Reservation" = 1L, .default = NA_integer_),
  )


df <- 
  read_dta(here::here("data", "all_appended.dta")) %>% 
  distinct(stdid, course_name, facid, .keep_all = T) %>% 
  left_join(
    df_stu %>% 
      select(stdid, classid, department_id, reservation, caste, ea_stud_group_criteria, grade),
    by = "stdid"
  ) %>%
  filter(ea_stud_group_criteria == 2, grade == 2) %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid")


# fixing for course cleaning done by sk in sep 2021
df <-
  df %>% 
  left_join(
    read_dta(here::here("data/students_clean.dta")),
    by = c("department_id", "course_name")
  ) %>% 
  mutate(
    course_name = if_else(!is.na(course_clean_sk), course_clean_sk, course_name)
  ) %>%
  distinct(stdid, course_name, facid, .keep_all = T)
```



```{r}
# grade data after veda's work
df_grades <-
  read_dta(here::here("data/30jan2022/df_gradefac.dta")) %>% 
  filter(facid != "") %>%
  left_join(df_stu %>% select(stdid, department_id, reservation, caste, b_i_jeemain_score, b_math_g1_score, b_physics_g1_score, b_ses_1, b_ses_2, b_ses_3, b_ses_4, b_ses_5, b_ses_6, b_i_ses_1, b_i_ses_2, b_i_ses_3, b_ct_score, b_ql_score, b_i_enter_engineering_exam), by = "stdid") %>%
  left_join(read_dta(here::here("data/controls.dta")), by = "stdid") %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid") %>% 
  arrange(department_id, course_name, course_grade_clean) %>% 
  group_by(department_id, course_name) %>% 
  mutate(
    course_rank = (scale(course_grade_clean) %>% pnorm() * 100) %>% as.vector
  ) %>% 
  ungroup() %>%
  mutate(
    univcode = str_sub(department_id, 1, 5),
    father_college = if_else(father_ed_ind > 3 & !is.na(father_ed_ind), 1L, 0L),
    father_college = if_else(is.na(father_ed_ind), NA_integer_, father_college),
    mother_college = if_else(mother_ed_ind > 3 & !is.na(mother_ed_ind), 1L, 0L),
    mother_college = if_else(is.na(mother_ed_ind), NA_integer_, mother_college),
    female = female %>% as.integer(),
    age = age %>% as.integer(),
  ) %>%
  fastDummies::dummy_cols(select_columns = c("b_i_enter_engineering_exam", "hstype", "area", "father_ed_ind", "mother_ed_ind"), remove_first_dummy = T, ignore_na = F) %>%
  relocate(department_id, course_name, stdid, course_rank) %>% 
  rename(reservation_stu = reservation) %>%
  filter(univcode != "IR036") %>% 
  mutate(
    
    # student variables
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0L, age),
    
    miss_reservation_stu = if_else(is.na(reservation_stu), 1L, 0L),
    reservation_stu = if_else(is.na(reservation_stu), 0L, reservation_stu),
    
    miss_father_college = if_else(is.na(father_college), 1L, 0L),
    father_college = if_else(is.na(father_college), 0L, father_college),
    
    miss_mother_college = if_else(is.na(mother_college), 1L, 0L),
    mother_college = if_else(is.na(mother_college), 0L, mother_college),
    
    miss_b_i_jeemain_score = if_else(is.na(b_i_jeemain_score), 1L, 0L),
    b_i_jeemain_score = if_else(is.na(b_i_jeemain_score), 0, b_i_jeemain_score),
    
    miss_b_math_g1_score = if_else(is.na(b_math_g1_score), 1L, 0L),
    b_math_g1_score = if_else(is.na(b_math_g1_score), 0, b_math_g1_score),
    
    miss_b_physics_g1_score = if_else(is.na(b_physics_g1_score), 1L, 0L),
    b_physics_g1_score = if_else(is.na(b_physics_g1_score), 0, b_physics_g1_score),
    
    miss_b_ct_score = if_else(is.na(b_ct_score), 1L, 0L),
    b_ct_score = if_else(is.na(b_ct_score), 0, b_ct_score),
    
    miss_b_ql_score = if_else(is.na(b_ql_score), 1L, 0L),
    b_ql_score = if_else(is.na(b_ql_score), 0, b_ql_score),
    
    # faculty variables
    miss_fac_associate_professor = if_else(is.na(fac_associate_professor), 1L, 0L),
    fac_associate_professor = if_else(is.na(fac_associate_professor), 0, fac_associate_professor),
    
    miss_fac_professor = if_else(is.na(fac_professor), 1L, 0L),
    fac_professor = if_else(is.na(fac_professor), 0, fac_professor),
    
    miss_fac_yearsinhighed = if_else(is.na(fac_yearsinhighed), 1L, 0L),
    fac_yearsinhighed = if_else(is.na(fac_yearsinhighed), 0, fac_yearsinhighed),
    
    miss_fac_highest_degree_phd = if_else(is.na(fac_highest_degree_phd), 1L, 0L),
    fac_highest_degree_phd = if_else(is.na(fac_highest_degree_phd), 0, fac_highest_degree_phd),
    
    miss_fac_highest_degree_phd_in_prog = if_else(is.na(fac_highest_degree_phd_in_prog), 1L, 0L),
    fac_highest_degree_phd_in_prog = if_else(is.na(fac_highest_degree_phd_in_prog), 0, fac_highest_degree_phd_in_prog),
    
    miss_fac_degree_college_elite = if_else(is.na(fac_degree_college_elite), 1L, 0L),
    fac_degree_college_elite = if_else(is.na(fac_degree_college_elite), 0, fac_degree_college_elite),
    
    miss_reservation_fac = if_else(is.na(reservation_fac), 1L, 0L),
    reservation_fac = if_else(is.na(reservation_fac), 0, reservation_fac)
  ) %>% 
  mutate_at(vars(b_ses_1, b_ses_2, b_ses_3, b_ses_4, b_ses_5, b_ses_6, b_i_ses_1, b_i_ses_2, b_i_ses_3), ~ as.integer(.)) %>%
  mutate(
    b_ses_1 = if_else(b_ses_1 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_2 = if_else(b_ses_2 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_3 = if_else(b_ses_3 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_4 = if_else(b_ses_4 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_5 = if_else(b_ses_5 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_6 = if_else(b_ses_6 == 1L, 1L, 0L) %>% replace_na(0L),
    b_i_ses_1 = if_else(b_i_ses_1 == 1L, 1L, 0L) %>% replace_na(0L),
    b_i_ses_2 = if_else(b_i_ses_2 == 1L, 1L, 0L) %>% replace_na(0L),
    b_i_ses_3 = if_else(b_i_ses_3 == 1L, 1L, 0L) %>% replace_na(0L),
  ) %>%
  mutate(
    old_sib_factor = case_when(
      old_sib == 0 ~ "0",
      old_sib == 1 ~ "1",
      old_sib == 2 ~ "2",
      old_sib == 3 ~ "3",
      old_sib == 4 ~ "4",
      old_sib > 4 ~ "more",
      TRUE ~ NA_character_
    ) %>% as_factor(),
    young_sib_factor = case_when(
      young_sib == 0 ~ "0",
      young_sib == 1 ~ "1",
      young_sib == 2 ~ "2",
      young_sib == 3 ~ "3",
      young_sib == 4 ~ "4",
      young_sib > 4 ~ "more",
      TRUE ~ NA_character_
    ) %>% as_factor(),
    school_years_english_factor = case_when(
      school_years_english == 0 ~ "0",
      school_years_english >= 1 & school_years_english <= 9 ~ "1-9",
      school_years_english >= 10 & school_years_english <= 12 ~ "10-12",
      school_years_english >= 13 & school_years_english <= 16 ~ "13-16",
      TRUE ~ NA_character_
    ) %>% as_factor(),
  ) %>%
  fastDummies::dummy_cols(select_columns = c("old_sib_factor", "young_sib_factor", "school_years_english_factor"), remove_first_dummy = T, ignore_na = F, remove_selected_columns = T) %>%
  mutate_at(vars(b_i_enter_engineering_exam_2, b_i_enter_engineering_exam_3, area_2, area_3, hstype_2, hstype_3, hstype_4, hstype_5, hstype_6, hstype_7, father_ed_ind_2, father_ed_ind_3, father_ed_ind_4, father_ed_ind_5, father_ed_ind_6, father_ed_ind_7, father_ed_ind_8, mother_ed_ind_2, mother_ed_ind_3, mother_ed_ind_4, mother_ed_ind_5, mother_ed_ind_6, mother_ed_ind_7, mother_ed_ind_8), ~ replace_na(., 0L)) %>% 
  mutate_at(vars(contains("_sib_factor_")), ~ replace_na(., 0L)) %>% 
  mutate_at(vars(contains("school_years_english_factor")), ~ replace_na(., 0L))
  
# df_grades %>% glimpse()
# df_grades %>% skim()

rm(df)
```


```{r}
# excluding students facing no gender variation
df_grades_sfix <-
  df_grades %>% 
  arrange(stdid, fac_female) %>% 
  group_by(stdid) %>% 
  mutate(prop_female = mean(fac_female, na.rm = T)) %>% 
  ungroup() %>% 
  relocate(stdid, fac_female, prop_female) %>%
  filter(prop_female > 0, prop_female < 1)
```


## Iteration 8

Model controls: 

- Student: reservation status, age, father attended college, mother attended college, jee main score, math test score, physics test score, SES dummies, CT test score, QL test score, type of college admission test taken (JEE Main, state-level, private), domicile area (rural, urban, urban slum), type of high school attended, granular father and mother education levels, younger siblings, older siblings, and years spent in english medium school.
- Faculty: faculty associate professor, faculty professor, faculty years in higher ed, faculty highest degree is phd, faculty highest degree is phd in progress, faculty degree college is elite, faculty reservation status


```{r, results='asis'}
lm1 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm2 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3 + b_ct_score + b_ql_score + miss_b_ct_score + miss_b_ql_score + b_i_enter_engineering_exam_2 + b_i_enter_engineering_exam_3 + b_i_enter_engineering_exam_NA + area_2 + area_3 + area_NA + hstype_2 + hstype_3 + hstype_4 + hstype_5 + hstype_6 + hstype_7 + hstype_NA + father_ed_ind_2 + father_ed_ind_3 + father_ed_ind_4 + father_ed_ind_5 + father_ed_ind_6 + father_ed_ind_7 + father_ed_ind_8 + father_ed_ind_NA + mother_ed_ind_2 + mother_ed_ind_3 + mother_ed_ind_4 + mother_ed_ind_5 + mother_ed_ind_6 + mother_ed_ind_7 + mother_ed_ind_8 + mother_ed_ind_NA + old_sib_factor_0 + old_sib_factor_2 + old_sib_factor_3 + old_sib_factor_4 + old_sib_factor_more + old_sib_factor_NA + young_sib_factor_0 + young_sib_factor_2 + young_sib_factor_3 + young_sib_factor_4 + young_sib_factor_more + young_sib_factor_NA + `school_years_english_factor_1-9` + `school_years_english_factor_10-12` + `school_years_english_factor_13-16` + school_years_english_factor_NA, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm3 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3 + b_ct_score + b_ql_score + miss_b_ct_score + miss_b_ql_score + b_i_enter_engineering_exam_2 + b_i_enter_engineering_exam_3 + b_i_enter_engineering_exam_NA + area_2 + area_3 + area_NA + hstype_2 + hstype_3 + hstype_4 + hstype_5 + hstype_6 + hstype_7 + hstype_NA + father_ed_ind_2 + father_ed_ind_3 + father_ed_ind_4 + father_ed_ind_5 + father_ed_ind_6 + father_ed_ind_7 + father_ed_ind_8 + father_ed_ind_NA + mother_ed_ind_2 + mother_ed_ind_3 + mother_ed_ind_4 + mother_ed_ind_5 + mother_ed_ind_6 + mother_ed_ind_7 + mother_ed_ind_8 + mother_ed_ind_NA + old_sib_factor_0 + old_sib_factor_2 + old_sib_factor_3 + old_sib_factor_4 + old_sib_factor_more + old_sib_factor_NA + young_sib_factor_0 + young_sib_factor_2 + young_sib_factor_3 + young_sib_factor_4 + young_sib_factor_more + young_sib_factor_NA + `school_years_english_factor_1-9` + `school_years_english_factor_10-12` + `school_years_english_factor_13-16` + school_years_english_factor_NA, data = ., fixed_effects = ~ fe_var + stdid, se_type = "stata")

lm4 <-
  df_grades %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3 + b_ct_score + b_ql_score + miss_b_ct_score + miss_b_ql_score + b_i_enter_engineering_exam_2 + b_i_enter_engineering_exam_3 + b_i_enter_engineering_exam_NA + area_2 + area_3 + area_NA + hstype_2 + hstype_3 + hstype_4 + hstype_5 + hstype_6 + hstype_7 + hstype_NA + father_ed_ind_2 + father_ed_ind_3 + father_ed_ind_4 + father_ed_ind_5 + father_ed_ind_6 + father_ed_ind_7 + father_ed_ind_8 + father_ed_ind_NA + mother_ed_ind_2 + mother_ed_ind_3 + mother_ed_ind_4 + mother_ed_ind_5 + mother_ed_ind_6 + mother_ed_ind_7 + mother_ed_ind_8 + mother_ed_ind_NA + old_sib_factor_0 + old_sib_factor_2 + old_sib_factor_3 + old_sib_factor_4 + old_sib_factor_more + old_sib_factor_NA + young_sib_factor_0 + young_sib_factor_2 + young_sib_factor_3 + young_sib_factor_4 + young_sib_factor_more + young_sib_factor_NA + `school_years_english_factor_1-9` + `school_years_english_factor_10-12` + `school_years_english_factor_13-16` + school_years_english_factor_NA, data = ., fixed_effects = ~ fe_var + stdid + facid, se_type = "stata")

lm5 <-
  df_grades %>%
  mutate(
    fe_var = str_c(department_id, course_name, sep = "_"),
    class_fe_var = str_c(fe_var, facid, sep = "_")
  ) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3 + b_ct_score + b_ql_score + miss_b_ct_score + miss_b_ql_score + b_i_enter_engineering_exam_2 + b_i_enter_engineering_exam_3 + b_i_enter_engineering_exam_NA + area_2 + area_3 + area_NA + hstype_2 + hstype_3 + hstype_4 + hstype_5 + hstype_6 + hstype_7 + hstype_NA + father_ed_ind_2 + father_ed_ind_3 + father_ed_ind_4 + father_ed_ind_5 + father_ed_ind_6 + father_ed_ind_7 + father_ed_ind_8 + father_ed_ind_NA + mother_ed_ind_2 + mother_ed_ind_3 + mother_ed_ind_4 + mother_ed_ind_5 + mother_ed_ind_6 + mother_ed_ind_7 + mother_ed_ind_8 + mother_ed_ind_NA + old_sib_factor_0 + old_sib_factor_2 + old_sib_factor_3 + old_sib_factor_4 + old_sib_factor_more + old_sib_factor_NA + young_sib_factor_0 + young_sib_factor_2 + young_sib_factor_3 + young_sib_factor_4 + young_sib_factor_more + young_sib_factor_NA + `school_years_english_factor_1-9` + `school_years_english_factor_10-12` + `school_years_english_factor_13-16` + school_years_english_factor_NA, data = ., fixed_effects = ~ fe_var + stdid + class_fe_var, se_type = "stata")

knitreg(list(lm1, lm2, lm3, lm4, lm5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, custom.coef.map = list("female:fac_female" = "Stu Female x Fac Female"))
```

