---
title: "Tables for Gender Paper"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: ["dcolumn", "booktabs", "caption", "float"]
    toc: yes
    toc_depth: 6
    keep_tex: yes
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(haven, estimatr, extrafont, texreg, janitor, hrbrthemes, xtable, papeR, tidyverse, compareGroups, Hmisc, skimr)
```


# Defining models

- Model 1: student female, faculty female, gender student*gender faculty interaction, course fes (level of randomization)
- Model 2: add student controls and faculty controls to Model 1
- Model 3: add student fes to Model 2 (student controls drop out)
- Model 4: add faculty fes to Model 3 (faculty controls drop out)
- Model 5: add classroom fes to Model 4 (faculty fes should drop out)

\newpage

# Main Tables

```{r}
# Student Data
df_stu <- 
  read_dta(here::here("data", "stu_admin_all_latest.dta")) %>%
  left_join(read_dta(here::here("data/reservation_new.dta")), by = "stdid") %>% 
  mutate(
    reservation = dplyr::recode(reservation, "Non-reservation" = 0L, "Reservation" = 1L, .default = NA_integer_),
  )


df <- 
  read_dta(here::here("data", "all_appended.dta")) %>% 
  distinct(stdid, course_name, facid, .keep_all = T) %>% 
  left_join(
    df_stu %>% 
      select(stdid, classid, department_id, reservation, caste, ea_stud_group_criteria, grade),
    by = "stdid"
  ) %>%
  filter(ea_stud_group_criteria == 2, grade == 2) %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid")


# fixing for course cleaning done by sk in sep 2021
df <-
  df %>% 
  left_join(
    read_dta(here::here("data/students_clean.dta")),
    by = c("department_id", "course_name")
  ) %>% 
  mutate(
    course_name = if_else(!is.na(course_clean_sk), course_clean_sk, course_name)
  ) %>%
  distinct(stdid, course_name, facid, .keep_all = T)
```



```{r}
# grade data after veda's work
df_grades <-
  read_dta(here::here("data/30jan2022/df_gradefac.dta")) %>% 
  filter(facid != "") %>%
  left_join(df_stu %>% select(stdid, department_id, reservation, caste, b_i_jeemain_score, b_math_g1_score, b_physics_g1_score, b_ses_1, b_ses_2, b_ses_3, b_ses_4, b_ses_5, b_ses_6, b_i_ses_1, b_i_ses_2, b_i_ses_3), by = "stdid") %>%
  left_join(read_dta(here::here("data/controls.dta")), by = "stdid") %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid") %>% 
  arrange(department_id, course_name, course_grade_clean) %>% 
  group_by(department_id, course_name) %>% 
  mutate(
    course_rank = (scale(course_grade_clean) %>% pnorm() * 100) %>% as.vector
  ) %>% 
  ungroup() %>%
  mutate(
    father_college = if_else(father_ed_ind > 3 & !is.na(father_ed_ind), 1L, 0L),
    father_college = if_else(is.na(father_ed_ind), NA_integer_, father_college),
    mother_college = if_else(mother_ed_ind > 3 & !is.na(mother_ed_ind), 1L, 0L),
    mother_college = if_else(is.na(mother_ed_ind), NA_integer_, mother_college),
    ses = ses %>% as.integer(),
    female = female %>% as.integer(),
    age = age %>% as.integer(),
    univcode = str_sub(department_id, 1, 5),
  ) %>%
  relocate(department_id, course_name, stdid, course_rank) %>% 
  rename(reservation_stu = reservation, fac_teaching = fac_tpi_score7_z) %>% 
  filter(univcode != "IR036") %>% 
  mutate(
    
    # student variables
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0L, age),
    
    miss_reservation_stu = if_else(is.na(reservation_stu), 1L, 0L),
    reservation_stu = if_else(is.na(reservation_stu), 0L, reservation_stu),
    
    miss_father_college = if_else(is.na(father_college), 1L, 0L),
    father_college = if_else(is.na(father_college), 0L, father_college),
    
    miss_mother_college = if_else(is.na(mother_college), 1L, 0L),
    mother_college = if_else(is.na(mother_college), 0L, mother_college),
    
    miss_b_i_jeemain_score = if_else(is.na(b_i_jeemain_score), 1L, 0L),
    b_i_jeemain_score = if_else(is.na(b_i_jeemain_score), 0, b_i_jeemain_score),
    
    miss_b_math_g1_score = if_else(is.na(b_math_g1_score), 1L, 0L),
    b_math_g1_score = if_else(is.na(b_math_g1_score), 0, b_math_g1_score),
    
    miss_b_physics_g1_score = if_else(is.na(b_physics_g1_score), 1L, 0L),
    b_physics_g1_score = if_else(is.na(b_physics_g1_score), 0, b_physics_g1_score),
    
    # faculty variables
    miss_fac_associate_professor = if_else(is.na(fac_associate_professor), 1L, 0L),
    fac_associate_professor = if_else(is.na(fac_associate_professor), 0, fac_associate_professor),
    
    miss_fac_professor = if_else(is.na(fac_professor), 1L, 0L),
    fac_professor = if_else(is.na(fac_professor), 0, fac_professor),
    
    miss_fac_yearsinhighed = if_else(is.na(fac_yearsinhighed), 1L, 0L),
    fac_yearsinhighed = if_else(is.na(fac_yearsinhighed), 0, fac_yearsinhighed),
    
    miss_fac_highest_degree_phd = if_else(is.na(fac_highest_degree_phd), 1L, 0L),
    fac_highest_degree_phd = if_else(is.na(fac_highest_degree_phd), 0, fac_highest_degree_phd),
    
    miss_fac_highest_degree_phd_in_prog = if_else(is.na(fac_highest_degree_phd_in_prog), 1L, 0L),
    fac_highest_degree_phd_in_prog = if_else(is.na(fac_highest_degree_phd_in_prog), 0, fac_highest_degree_phd_in_prog),
    
    miss_fac_degree_college_elite = if_else(is.na(fac_degree_college_elite), 1L, 0L),
    fac_degree_college_elite = if_else(is.na(fac_degree_college_elite), 0, fac_degree_college_elite),
    
    miss_reservation_fac = if_else(is.na(reservation_fac), 1L, 0L),
    reservation_fac = if_else(is.na(reservation_fac), 0, reservation_fac)
  ) %>% 
  mutate_at(vars(b_ses_1, b_ses_2, b_ses_3, b_ses_4, b_ses_5, b_ses_6, b_i_ses_1, b_i_ses_2, b_i_ses_3), ~ as.integer(.)) %>%
  mutate(
    b_ses_1 = if_else(b_ses_1 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_2 = if_else(b_ses_2 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_3 = if_else(b_ses_3 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_4 = if_else(b_ses_4 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_5 = if_else(b_ses_5 == 1L, 1L, 0L) %>% replace_na(0L),
    b_ses_6 = if_else(b_ses_6 == 1L, 1L, 0L) %>% replace_na(0L),
    b_i_ses_1 = if_else(b_i_ses_1 == 1L, 1L, 0L) %>% replace_na(0L),
    b_i_ses_2 = if_else(b_i_ses_2 == 1L, 1L, 0L) %>% replace_na(0L),
    b_i_ses_3 = if_else(b_i_ses_3 == 1L, 1L, 0L) %>% replace_na(0L)
  )
  
# df_grades %>% drop_na() %>% glimpse()
# df_grades %>% skim()

rm(df)
```


```{r}
# excluding students facing no gender variation
df_grades_sfix <-
  df_grades %>% 
  arrange(stdid, fac_female) %>% 
  group_by(stdid) %>% 
  mutate(prop_female = mean(fac_female, na.rm = T)) %>% 
  ungroup() %>% 
  relocate(stdid, fac_female, prop_female) %>%
  filter(prop_female > 0, prop_female < 1)

# excluding courses with no gender variation
df_grades_cfix <-
  df_grades %>% 
  mutate(course_composite = str_c(department_id, course_name, sep = "_")) %>%
  arrange(course_composite, fac_female) %>% 
  group_by(course_composite) %>% 
  mutate(prop_female = mean(fac_female, na.rm = T)) %>% 
  ungroup() %>% 
  relocate(course_composite, fac_female, prop_female) %>%
  filter(prop_female > 0, prop_female < 1)

# excluding both courses and students with no gender variation
df_grades_csfix <-
  df_grades_cfix %>% 
  select(-prop_female) %>% 
  group_by(stdid) %>% 
  mutate(prop_female = mean(fac_female, na.rm = T)) %>% 
  ungroup() %>% 
  filter(prop_female > 0, prop_female < 1)
```


No rows dropped:

```{r, results='asis'}
lm1 <-
  df_grades %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm2 <-
  df_grades %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm3 <-
  df_grades %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid, se_type = "stata")

lm4 <-
  df_grades %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + facid, se_type = "stata")

lm5 <-
  df_grades %>%
  mutate(
    fe_var = str_c(department_id, course_name, sep = "_"),
    class_fe_var = str_c(fe_var, facid, sep = "_")
  ) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + class_fe_var, se_type = "stata")

knitreg(list(lm1, lm2, lm3, lm4, lm5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, custom.coef.map = list("female:fac_female" = "Stu Female x Fac Female"))
```


Students with no variation in faculty gender dropped:

```{r, results='asis'}
lm1 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm2 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm3 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid, se_type = "stata")

lm4 <-
  df_grades_sfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + facid, se_type = "stata")

lm5 <-
  df_grades_sfix %>%
  mutate(
    fe_var = str_c(department_id, course_name, sep = "_"),
    class_fe_var = str_c(fe_var, facid, sep = "_")
  ) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + class_fe_var, se_type = "stata")

knitreg(list(lm1, lm2, lm3, lm4, lm5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, custom.coef.map = list("female:fac_female" = "Stu Female x Fac Female"))
```


Courses with no variation in faculty gender dropped:


```{r, results='asis'}
lm1 <-
  df_grades_cfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm2 <-
  df_grades_cfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm3 <-
  df_grades_cfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid, se_type = "stata")

lm4 <-
  df_grades_cfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + facid, se_type = "stata")

lm5 <-
  df_grades_cfix %>%
  mutate(
    fe_var = str_c(department_id, course_name, sep = "_"),
    class_fe_var = str_c(fe_var, facid, sep = "_")
  ) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + class_fe_var, se_type = "stata")

knitreg(list(lm1, lm2, lm3, lm4, lm5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, custom.coef.map = list("female:fac_female" = "Stu Female x Fac Female"))
```


Course with no variation dropped, then students with no variation dropped:

```{r, results='asis'}
lm1 <-
  df_grades_csfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm2 <-
  df_grades_csfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var, se_type = "stata")

lm3 <-
  df_grades_csfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid, se_type = "stata")

lm4 <-
  df_grades_csfix %>%
  mutate(fe_var = str_c(department_id, course_name, sep = "_")) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + facid, se_type = "stata")

lm5 <-
  df_grades_csfix %>%
  mutate(
    fe_var = str_c(department_id, course_name, sep = "_"),
    class_fe_var = str_c(fe_var, facid, sep = "_")
  ) %>%
  lm_robust(course_rank ~ female * fac_female + reservation_stu + age + father_college + mother_college + b_i_jeemain_score + b_math_g1_score + b_physics_g1_score + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + reservation_fac + miss_reservation_stu + miss_age + miss_father_college + miss_mother_college + miss_b_i_jeemain_score + miss_b_math_g1_score + miss_b_physics_g1_score +  miss_fac_associate_professor + miss_fac_professor + miss_fac_yearsinhighed + miss_fac_highest_degree_phd + miss_fac_highest_degree_phd_in_prog + miss_fac_degree_college_elite + miss_reservation_fac + b_ses_1 + b_ses_2 + b_ses_3 + b_ses_4 + b_ses_5 + b_ses_6 + b_i_ses_1 + b_i_ses_2 + b_i_ses_3, data = ., fixed_effects = ~ fe_var + stdid + class_fe_var, se_type = "stata")

knitreg(list(lm1, lm2, lm3, lm4, lm5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, custom.coef.map = list("female:fac_female" = "Stu Female x Fac Female"))
```


