---
title: "Faculty Productivity Results for Caste Paper"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: ["dcolumn", "booktabs", "caption", "float"]
    toc: yes
    toc_depth: 6
    keep_tex: yes
    number_sections: true
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
## Libraries
pacman::p_load(haven, estimatr, extrafont, texreg, janitor, xtable, papeR, tidyverse, compareGroups, Hmisc, skimr)
```

\newpage


# New tables

## International Publications per year (SCI + EI + SSCI)

These regressions use department-level sampling weights, and are run at the faculty level for the national sample (50 colleges). All specifications include college and department fixed effects. Dependent variable mean is 0.532, and is capped at max 10 per year.

```{=latex}
\begin{table}[H]
\begin{center}
\begin{tabular}{l D{.}{.}{4.5} D{.}{.}{4.7} D{.}{.}{4.7} D{.}{.}{4.7}}
\toprule
 & \multicolumn{1}{c}{I} & \multicolumn{1}{c}{II} & \multicolumn{1}{c}{III} & \multicolumn{1}{c}{IV} \\
\midrule
Reservation faculty               & -0.0541  & 0.0036       & 0.0037       & -0.0031      \\
                                  & (0.0427) & (0.0417)     & (0.0413)     & (0.0407)     \\
Associate professor               &          & 0.2106^{***} & 0.1301^{*}   & 0.1336^{**}  \\
                                  &          & (0.0744)     & (0.0681)     & (0.0667)     \\
Professor                         &          & 0.9432^{***} & 0.7717^{***} & 0.7622^{***} \\
                                  &          & (0.2142)     & (0.2141)     & (0.2134)     \\
Experience in years               &          & 0.0106^{**}  & 0.0081       & 0.0078       \\
                                  &          & (0.0053)     & (0.0054)     & (0.0053)     \\
Highest degree is PhD             &          &              & 0.2517^{***} & 0.2554^{***} \\
                                  &          &              & (0.0760)     & (0.0743)     \\
Highest degree is PhD in progress &          &              & 0.0084       & 0.0061       \\
                                  &          &              & (0.0368)     & (0.0368)     \\
Degree college elite              &          &              & 0.0874^{*}   & 0.0844       \\
                                  &          &              & (0.0527)     & (0.0522)     \\
Female                            &          &              &              & -0.0648^{**} \\
                                  &          &              &              & (0.0294)     \\
\midrule
Num. obs.                         & 2691     & 2685         & 2680         & 2679         \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\caption{}
\label{table:coefficients}
\end{center}
\end{table}
```


\newpage

## Funding

These regressions use department-level sampling weights, and are run at the faculty level for the national sample (50 colleges). All specifications include college and department fixed effects.

### Government funding (0/1)

Dependent variable mean is 0.097.

```{=latex}
\begin{table}[H]
\begin{center}
\begin{tabular}{l D{.}{.}{4.5} D{.}{.}{4.7} D{.}{.}{4.7} D{.}{.}{4.7}}
\toprule
 & \multicolumn{1}{c}{I} & \multicolumn{1}{c}{II} & \multicolumn{1}{c}{III} & \multicolumn{1}{c}{IV} \\
\midrule
Reservation faculty               & -0.0059  & 0.0026       & 0.0018       & 0.0010       \\
                                  & (0.0090) & (0.0085)     & (0.0086)     & (0.0084)     \\
Associate professor               &          & 0.0253       & 0.0164       & 0.0168       \\
                                  &          & (0.0159)     & (0.0172)     & (0.0171)     \\
Professor                         &          & 0.1536^{***} & 0.1353^{***} & 0.1341^{***} \\
                                  &          & (0.0352)     & (0.0358)     & (0.0358)     \\
Experience in years               &          & 0.0010       & 0.0011       & 0.0010       \\
                                  &          & (0.0009)     & (0.0009)     & (0.0009)     \\
Highest degree is PhD             &          &              & 0.0212       & 0.0217       \\
                                  &          &              & (0.0169)     & (0.0168)     \\
Highest degree is PhD in progress &          &              & -0.0184^{**} & -0.0186^{**} \\
                                  &          &              & (0.0093)     & (0.0093)     \\
Degree college elite              &          &              & -0.0120      & -0.0124      \\
                                  &          &              & (0.0117)     & (0.0117)     \\
Female                            &          &              &              & -0.0077      \\
                                  &          &              &              & (0.0080)     \\
\midrule
Num. obs.                         & 2691     & 2685         & 2680         & 2679         \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\caption{}
\label{}
\end{center}
\end{table}
```


\newpage

### Private funding (0/1)

Dependent variable mean is 0.029.

```{=latex}
\begin{table}[H]
\begin{center}
\begin{tabular}{l D{.}{.}{4.5} D{.}{.}{4.5} D{.}{.}{4.6} D{.}{.}{4.7}}
\toprule
 & \multicolumn{1}{c}{I} & \multicolumn{1}{c}{II} & \multicolumn{1}{c}{III} & \multicolumn{1}{c}{IV} \\
\midrule
Reservation faculty               & -0.0021  & -0.0006  & -0.0003     & -0.0024       \\
                                  & (0.0074) & (0.0077) & (0.0077)    & (0.0078)      \\
Associate professor               &          & -0.0039  & -0.0131     & -0.0121       \\
                                  &          & (0.0100) & (0.0112)    & (0.0112)      \\
Professor                         &          & 0.0216   & 0.0036      & 0.0006        \\
                                  &          & (0.0211) & (0.0222)    & (0.0222)      \\
Experience in years               &          & 0.0007   & 0.0005      & 0.0004        \\
                                  &          & (0.0007) & (0.0007)    & (0.0007)      \\
Highest degree is PhD             &          &          & 0.0323^{**} & 0.0334^{**}   \\
                                  &          &          & (0.0143)    & (0.0143)      \\
Highest degree is PhD in progress &          &          & 0.0128      & 0.0121        \\
                                  &          &          & (0.0086)    & (0.0086)      \\
Degree college elite              &          &          & -0.0105^{*} & -0.0114^{*}   \\
                                  &          &          & (0.0062)    & (0.0062)      \\
Female                            &          &          &             & -0.0200^{***} \\
                                  &          &          &             & (0.0062)      \\
\midrule
Num. obs.                         & 2691     & 2685     & 2680        & 2679          \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\caption{}
\label{table:coefficients}
\end{center}
\end{table}
```

\newpage

## Faculty research, position, and funding models

Models below are run at the student-course level, and control for student fixed effects and course fixed effects. Standard errors are clustered at faculty level. Dependent variables are:

- Model I: Total annual publications (capped at max 10)
- Model II: Total annual international publications (capped at max 10)
- Model III: Total annual international SCI/EI/SSCI publications (capped at max 10)
- Model IV: Funding received (0/1)
- Model V: Admin position held (0/1)

```{=latex}
\begin{table}[H]
\begin{center}
\begin{tabular}{l D{.}{.}{5.5} D{.}{.}{5.5} D{.}{.}{5.4} D{.}{.}{5.5} D{.}{.}{5.5}}
\toprule
 & \multicolumn{1}{c}{I} & \multicolumn{1}{c}{II} & \multicolumn{1}{c}{III} & \multicolumn{1}{c}{IV} & \multicolumn{1}{c}{V} \\
\midrule
reservation\_fac                    & -0.37      & -0.29^{**} & -0.10     & -0.03       & 0.03       \\
                                    & (0.27)     & (0.14)     & (0.09)    & (0.02)      & (0.05)     \\
fac\_associate\_professor           & 1.11^{***} & 0.92^{***} & 0.33^{**} & 0.07        & 0.01       \\
                                    & (0.37)     & (0.20)     & (0.16)    & (0.07)      & (0.07)     \\
fac\_professor                      & 1.80^{***} & 1.16^{***} & 0.72^{**} & -0.01       & 0.02       \\
                                    & (0.69)     & (0.45)     & (0.31)    & (0.07)      & (0.11)     \\
fac\_yearsinhighed                  & -0.06^{**} & -0.02^{*}  & -0.02^{*} & 0.00        & 0.02^{***} \\
                                    & (0.03)     & (0.01)     & (0.01)    & (0.00)      & (0.00)     \\
fac\_highest\_degree\_phd           & 2.37^{***} & 0.92^{***} & 0.66^{**} & 0.23^{***}  & 0.19^{*}   \\
                                    & (0.78)     & (0.29)     & (0.26)    & (0.07)      & (0.11)     \\
fac\_highest\_degree\_phd\_in\_prog & 1.06^{***} & 0.53^{***} & 0.12      & 0.01        & -0.11^{*}  \\
                                    & (0.39)     & (0.17)     & (0.11)    & (0.03)      & (0.06)     \\
fac\_degree\_college\_elite         & 0.16       & 0.00       & 0.00      & -0.09^{***} & 0.00       \\
                                    & (0.32)     & (0.18)     & (0.12)    & (0.04)      & (0.06)     \\
fac\_female                         & -0.24      & -0.20      & -0.07     & 0.09^{***}  & 0.06       \\
                                    & (0.24)     & (0.12)     & (0.09)    & (0.03)      & (0.05)     \\
\midrule
Num. obs.                           & 37970      & 37970      & 37970     & 37970       & 37970      \\
\bottomrule
\multicolumn{6}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\caption{}
\label{table:coefficients}
\end{center}
\end{table}
```

\newpage

# Old table changes

## Total annual publications (Main Table 5.7)

Total annual publications updated as upper limit is 10 now. Dependent variable mean is 2.40. The regressions use department-level sampling weights, and are run at the faculty level for the national sample (50 colleges). All specifications include college and department fixed effects.

```{=latex}
\begin{table}[H]
\begin{center}
\begin{tabular}{l D{.}{.}{4.3} D{.}{.}{4.5} D{.}{.}{4.5} D{.}{.}{4.5}}
\toprule
 & \multicolumn{1}{c}{I} & \multicolumn{1}{c}{II} & \multicolumn{1}{c}{III} & \multicolumn{1}{c}{IV} \\
\midrule
Reservation faculty               & -0.12  & 0.07       & 0.09       & 0.06       \\
                                  & (0.12) & (0.10)     & (0.10)     & (0.11)     \\
Associate professor               &        & 0.63^{***} & 0.16       & 0.17       \\
                                  &        & (0.18)     & (0.20)     & (0.20)     \\
Professor                         &        & 2.49^{***} & 1.54^{***} & 1.51^{***} \\
                                  &        & (0.37)     & (0.39)     & (0.39)     \\
Experience in years               &        & 0.07^{***} & 0.05^{***} & 0.05^{***} \\
                                  &        & (0.01)     & (0.01)     & (0.01)     \\
Highest degree is PhD             &        &            & 1.66^{***} & 1.67^{***} \\
                                  &        &            & (0.21)     & (0.21)     \\
Highest degree is PhD in progress &        &            & 0.69^{***} & 0.69^{***} \\
                                  &        &            & (0.14)     & (0.14)     \\
Degree college elite              &        &            & -0.06      & -0.06      \\
                                  &        &            & (0.14)     & (0.14)     \\
Female                            &        &            &            & -0.20^{**} \\
                                  &        &            &            & (0.10)     \\
\midrule
Num. obs.                         & 2691   & 2685       & 2680       & 2679       \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\caption{}
\label{table:coefficients}
\end{center}
\end{table}
```

\newpage

## Total annual international publications (Main Table 5.8)

Total international publications updated as we mark missing values as 0 now, and upper limit is 10. Dependent variable mean is 0.98. The regressions use department-level sampling weights, and are run at the faculty level for the national sample (50 colleges). All specifications include college and department fixed effects.

```{=latex}
\begin{table}[H]
\begin{center}
\begin{tabular}{l D{.}{.}{4.3} D{.}{.}{4.5} D{.}{.}{4.5} D{.}{.}{4.5}}
\toprule
 & \multicolumn{1}{c}{I} & \multicolumn{1}{c}{II} & \multicolumn{1}{c}{III} & \multicolumn{1}{c}{IV} \\
\midrule
Reservation faculty               & -0.07  & 0.03       & 0.04       & 0.03       \\
                                  & (0.07) & (0.06)     & (0.06)     & (0.06)     \\
Associate professor               &        & 0.40^{***} & 0.19^{**}  & 0.19^{**}  \\
                                  &        & (0.11)     & (0.10)     & (0.10)     \\
Professor                         &        & 1.60^{***} & 1.18^{***} & 1.17^{***} \\
                                  &        & (0.28)     & (0.28)     & (0.27)     \\
Experience in years               &        & 0.02^{***} & 0.01^{**}  & 0.01^{**}  \\
                                  &        & (0.01)     & (0.01)     & (0.01)     \\
Highest degree is PhD             &        &            & 0.73^{***} & 0.74^{***} \\
                                  &        &            & (0.11)     & (0.11)     \\
Highest degree is PhD in progress &        &            & 0.28^{***} & 0.28^{***} \\
                                  &        &            & (0.06)     & (0.06)     \\
Degree college elite              &        &            & -0.08      & -0.08      \\
                                  &        &            & (0.07)     & (0.07)     \\
Female                            &        &            &            & -0.06      \\
                                  &        &            &            & (0.05)     \\
\midrule
Num. obs.                         & 2691   & 2685       & 2680       & 2679       \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\caption{}
\label{table:coefficients}
\end{center}
\end{table}
```
