---
title: "Long Term Outcomes for Caste Paper"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: ["dcolumn", "booktabs", "caption", "float"]
    toc: yes
    toc_depth: 6
    keep_tex: yes
    number_sections: true
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(haven, estimatr, extrafont, texreg, janitor, hrbrthemes, xtable, papeR, tidyverse, compareGroups, Hmisc, skimr)
```

\newpage


```{r}
# Student Data
df_stu <- 
  read_dta(here::here("data", "stu_admin_all_latest.dta")) %>%
  left_join(read_dta(here::here("data/reservation_new.dta")), by = "stdid") %>% 
  mutate(
    reservation = dplyr::recode(reservation, "Non-reservation" = 0L, "Reservation" = 1L, .default = NA_integer_),
  )


df <- 
  read_dta(here::here("data", "all_appended.dta")) %>% 
  distinct(stdid, course_name, facid, .keep_all = T) %>% 
  left_join(
    df_stu %>% 
      select(stdid, classid, department_id, reservation, caste, ea_stud_group_criteria, grade),
    by = "stdid"
  ) %>%
  filter(ea_stud_group_criteria == 2, grade == 2) %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid")


# fixing for course cleaning done by sk in sep 2021
df <-
  df %>% 
  left_join(
    read_dta(here::here("data/students_clean.dta")),
    by = c("department_id", "course_name")
  ) %>% 
  mutate(
    course_name = if_else(!is.na(course_clean_sk), course_clean_sk, course_name)
  ) %>%
  distinct(stdid, course_name, facid, .keep_all = T)


# grade data after veda's work
df_grades <-
  read_dta(here::here("data/30jan2022/df_gradefac.dta")) %>% 
  filter(facid != "") %>%
  left_join(df_stu %>% select(stdid, department_id, reservation, caste, b_i_jeemain_score, b_math_g1_score, b_physics_g1_score, e_math_g3_score, e_physics_g3_score, elite), by = "stdid") %>%
  left_join(read_dta(here::here("data/controls.dta")), by = "stdid") %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid") %>% 
  arrange(department_id, course_name, course_grade_clean) %>% 
  group_by(department_id, course_name) %>% 
  mutate(
    course_rank = (scale(course_grade_clean) %>% pnorm() * 100) %>% as.vector
  ) %>% 
  ungroup() %>%
  mutate(
    father_college = if_else(father_ed_ind > 3 & !is.na(father_ed_ind), 1L, 0L),
    father_college = if_else(is.na(father_ed_ind), NA_integer_, father_college),
    mother_college = if_else(mother_ed_ind > 3 & !is.na(mother_ed_ind), 1L, 0L),
    mother_college = if_else(is.na(mother_ed_ind), NA_integer_, mother_college),
    ses = ses %>% as.integer(),
  ) %>%
  relocate(department_id, course_name, stdid, course_rank) %>% 
  rename(reservation_stu = reservation, fac_teaching = fac_tpi_score7_z)

rm(df)
```


# Student level results

```{r, fig.retina=4}
df_temp <-
  df_grades %>%
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_math_g3_score, e_physics_g3_score) %>%
  group_by(stdid, reservation_stu, female, father_college, mother_college, b_math_g1_score, e_math_g3_score, b_physics_g1_score, e_physics_g3_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup() %>% 
  mutate(
    e_math_g3_score = scale(e_math_g3_score) %>% as.vector,
    e_physics_g3_score = scale(e_physics_g3_score) %>% as.vector,
    b_math_g1_score = scale(b_math_g1_score) %>% as.vector,
    b_physics_g1_score = scale(b_physics_g1_score) %>% as.vector,
  ) %>% 
  relocate(stdid, reservation_fac, e_math_g3_score, b_math_g1_score, e_physics_g3_score, b_physics_g1_score)

# df_temp %>% skim()

df_temp %>% 
  ggplot(aes(reservation_fac)) +
  geom_histogram(alpha = 0.85) +
  theme_minimal() +
  scale_x_continuous(labels = scales::percent) +
  labs(
    x = "% reservation instructors",
    y = "Count",
    subtitle = "Distribution of treatment (% reservation instructors) for 1115 students taking math/physics tests")
```

\newpage

## Math

### No baseline score controls, no department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_math_g3_score ~ reservation_fac, data = ., se_type = "stata")

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_math_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata")

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_math_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata")

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

### With baseline score controls, no department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_math_g3_score ~ reservation_fac + b_math_g1_score, data = ., se_type = "stata")

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_math_g3_score ~ reservation_fac + b_math_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata")

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_math_g3_score ~ reservation_fac + b_math_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata")

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F ,omit.coef = "(miss_age)|(Intercept)")
```

\newpage


### No baseline score controls, with department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_math_g3_score ~ reservation_fac, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_math_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_math_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

### With baseline score controls, with department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_math_g3_score ~ reservation_fac + b_math_g1_score, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_math_g3_score ~ reservation_fac + b_math_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_math_g3_score ~ reservation_fac + b_math_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F ,omit.coef = "(miss_age)|(Intercept)")
```

\newpage

## Physics

### No baseline score controls, no department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_physics_g3_score ~ reservation_fac, data = ., se_type = "stata")

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_physics_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata")

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_physics_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata")

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

### With baseline score controls, no department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_physics_g3_score ~ reservation_fac + b_physics_g1_score, data = ., se_type = "stata")

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_physics_g3_score ~ reservation_fac + b_physics_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata")

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_physics_g3_score ~ reservation_fac + b_physics_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata")

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F ,omit.coef = "(miss_age)|(Intercept)")
```

\newpage


### No baseline score controls, with department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_physics_g3_score ~ reservation_fac, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_physics_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_physics_g3_score ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

### With baseline score controls, with department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_physics_g3_score ~ reservation_fac + b_physics_g1_score, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_physics_g3_score ~ reservation_fac + b_physics_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>% 
  lm_robust(e_physics_g3_score ~ reservation_fac + b_physics_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F ,omit.coef = "(miss_age)|(Intercept)")
```

\newpage

# Student-Subject level results

```{r}
df_math <-
  df_grades %>%
  filter(subject == "math") %>% 
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_math_g3_score) %>%
  group_by(stdid, subject, reservation_stu, female, father_college, mother_college, b_math_g1_score, e_math_g3_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup() %>% 
  mutate(
    e_g3_score = scale(e_math_g3_score) %>% as.vector,
    b_g1_score = scale(b_math_g1_score) %>% as.vector,
  ) %>% 
  relocate(stdid, reservation_fac, e_g3_score, b_g1_score, e_math_g3_score, b_math_g1_score)

df_physics <-
  df_grades %>%
  filter(subject == "physics") %>% 
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_physics_g3_score) %>%
  group_by(stdid, subject, reservation_stu, female, father_college, mother_college, b_physics_g1_score, e_physics_g3_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>%
  ungroup() %>% 
  mutate(
    e_g3_score = scale(e_physics_g3_score) %>% as.vector,
    b_g1_score = scale(b_physics_g1_score) %>% as.vector,
  ) %>% 
  relocate(stdid, reservation_fac, e_g3_score, b_g1_score, e_physics_g3_score, b_physics_g1_score)

df_temp <-
  bind_rows(df_math, df_physics) %>% 
  arrange(stdid, subject) %>% 
  relocate(stdid, subject) %>% 
  mutate(subject = as_factor(str_to_title(subject)))
```


## No baseline score controls, no department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject, data = ., se_type = "stata")

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata")

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata")

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```


\newpage

## With baseline score controls, no department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score, data = ., se_type = "stata")

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata")

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata")

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```


\newpage


## No baseline score controls, with department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

## With baseline score controls, with department fixed effects

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```
