---
title: "Long Term Outcomes for Caste Paper"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: ["dcolumn", "booktabs", "caption", "float"]
    toc: yes
    toc_depth: 6
    keep_tex: yes
    number_sections: true
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(haven, estimatr, extrafont, texreg, janitor, hrbrthemes, xtable, papeR, tidyverse, compareGroups, Hmisc, skimr)
```

\newpage


```{r}
# Student Data
df_stu <- 
  read_dta(here::here("data", "stu_admin_all_latest.dta")) %>%
  left_join(read_dta(here::here("data/reservation_new.dta")), by = "stdid") %>% 
  mutate(
    reservation = dplyr::recode(reservation, "Non-reservation" = 0L, "Reservation" = 1L, .default = NA_integer_),
  )


df <- 
  read_dta(here::here("data", "all_appended.dta")) %>% 
  distinct(stdid, course_name, facid, .keep_all = T) %>% 
  left_join(
    df_stu %>% 
      select(stdid, classid, department_id, reservation, caste, ea_stud_group_criteria, grade),
    by = "stdid"
  ) %>%
  filter(ea_stud_group_criteria == 2, grade == 2) %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid")


# fixing for course cleaning done by sk in sep 2021
df <-
  df %>% 
  left_join(
    read_dta(here::here("data/students_clean.dta")),
    by = c("department_id", "course_name")
  ) %>% 
  mutate(
    course_name = if_else(!is.na(course_clean_sk), course_clean_sk, course_name)
  ) %>%
  distinct(stdid, course_name, facid, .keep_all = T)
```



```{r}
# grade data after veda's work
df_grades <-
  read_dta(here::here("data/30jan2022/df_gradefac.dta")) %>% 
  filter(facid != "") %>%
  left_join(df_stu %>% select(stdid, department_id, reservation, caste, b_i_jeemain_score, b_math_g1_score, b_physics_g1_score, e_math_g3_score, e_physics_g3_score, b_ct_score, b_ql_score, e_ct_score, e_ql_score, b_rr_score, e_rr_score, e_attend_grad_school, e_college_satisfied, e_dropped_out), by = "stdid") %>%
  left_join(read_dta(here::here("data/controls.dta")), by = "stdid") %>%
  left_join(read_dta(here::here("data/fac_covariates.dta")), by = "facid") %>% 
  arrange(department_id, course_name, course_grade_clean) %>% 
  group_by(department_id, course_name) %>% 
  mutate(
    course_rank = (scale(course_grade_clean) %>% pnorm() * 100) %>% as.vector
  ) %>% 
  ungroup() %>%
  mutate(
    father_college = if_else(father_ed_ind > 3 & !is.na(father_ed_ind), 1L, 0L),
    father_college = if_else(is.na(father_ed_ind), NA_integer_, father_college),
    mother_college = if_else(mother_ed_ind > 3 & !is.na(mother_ed_ind), 1L, 0L),
    mother_college = if_else(is.na(mother_ed_ind), NA_integer_, mother_college),
    ses = ses %>% as.integer(),
  ) %>%
  relocate(department_id, course_name, stdid, course_rank) %>% 
  rename(reservation_stu = reservation)

rm(df)
```


# Test scores

## Math and Physics

```{r}
df_math <-
  df_grades %>%
  filter(subject == "math") %>% 
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_math_g3_score) %>%
  group_by(stdid, subject, reservation_stu, female, father_college, mother_college, b_math_g1_score, e_math_g3_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup() %>% 
  mutate(
    e_g3_score = scale(e_math_g3_score) %>% as.vector,
    b_g1_score = scale(b_math_g1_score) %>% as.vector,
  ) %>% 
  relocate(stdid, reservation_fac, e_g3_score, b_g1_score, e_math_g3_score, b_math_g1_score)

df_physics <-
  df_grades %>%
  filter(subject == "physics") %>% 
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_physics_g3_score) %>%
  group_by(stdid, subject, reservation_stu, female, father_college, mother_college, b_physics_g1_score, e_physics_g3_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>%
  ungroup() %>% 
  mutate(
    e_g3_score = scale(e_physics_g3_score) %>% as.vector,
    b_g1_score = scale(b_physics_g1_score) %>% as.vector,
  ) %>% 
  relocate(stdid, reservation_fac, e_g3_score, b_g1_score, e_physics_g3_score, b_physics_g1_score)

df_temp <-
  bind_rows(df_math, df_physics) %>% 
  arrange(stdid, subject) %>% 
  relocate(stdid, subject) %>% 
  mutate(subject = as_factor(str_to_title(subject)))

rm(df_math, df_physics)
```


All models include baseline score controls and department fixed effects.

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm4 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac * reservation_stu + subject + b_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3, lm4), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

## CT/QL and TORR

```{r}
df_ct <-
  df_grades %>%
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_ct_score) %>%
  group_by(stdid, reservation_stu, female, father_college, mother_college, b_ct_score, e_ct_score, b_rr_score, e_rr_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup() %>% 
  mutate(
    e_ct_score = scale(e_ct_score) %>% as.vector,
    b_ct_score = scale(b_ct_score) %>% as.vector,
    e_rr_score = scale(e_rr_score) %>% as.vector,
    b_rr_score = scale(b_rr_score) %>% as.vector,
  ) %>%
  pivot_longer(cols = c(e_ct_score, e_rr_score, b_ct_score, b_rr_score)) %>% 
  mutate(
    subject = str_sub(name, 3, 4) %>% str_to_upper(),
    name = if_else(str_detect(name, "^b_"), "b_score", "e_score")
  ) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  relocate(stdid, subject, e_score, b_score)

df_ql <-
  df_grades %>%
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>% 
  drop_na(e_ql_score) %>%
  group_by(stdid, reservation_stu, female, father_college, mother_college, b_ql_score, e_ql_score, b_rr_score, e_rr_score, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup() %>% 
  mutate(
    e_ql_score = scale(e_ql_score) %>% as.vector,
    b_ql_score = scale(b_ql_score) %>% as.vector,
    e_rr_score = scale(e_rr_score) %>% as.vector,
    b_rr_score = scale(b_rr_score) %>% as.vector,
  ) %>%
  pivot_longer(cols = c(e_ql_score, e_rr_score, b_ql_score, b_rr_score)) %>% 
  mutate(
    subject = str_sub(name, 3, 4) %>% str_to_upper(),
    name = if_else(str_detect(name, "^b_"), "b_score", "e_score")
  ) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  relocate(stdid, subject, e_score, b_score)

df_temp <-
  bind_rows(df_ct, df_ql) %>% 
  arrange(stdid, subject) %>% 
  rename(b_g1_score = b_score, e_g3_score = e_score) %>% 
  mutate(subject = fct_infreq(subject))

rm(df_ct, df_ql)
```


All models include baseline score controls and department fixed effects.

```{r, results='asis'}
lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac + subject + b_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm4 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_g3_score ~ reservation_fac * reservation_stu + subject + b_g1_score + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)


knitreg(list(lm1, lm2, lm3, lm4), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

# College satisfaction

All models include department fixed effects.

```{r, results='asis'}
df_temp <-
  df_grades %>%
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>%
  group_by(stdid, e_college_satisfied, reservation_stu, female, father_college, mother_college, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup()

lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_college_satisfied ~ reservation_fac, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_college_satisfied ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_college_satisfied ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm4 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_college_satisfied ~ reservation_fac * reservation_stu + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3, lm4), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```


\newpage

# Plans for grad school

All models include department fixed effects.

```{r, results='asis'}
df_temp <-
  df_grades %>%
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>%
  group_by(stdid, e_attend_grad_school, reservation_stu, female, father_college, mother_college, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup()

lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_attend_grad_school ~ reservation_fac, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_attend_grad_school ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_attend_grad_school ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm4 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_attend_grad_school ~ reservation_fac * reservation_stu + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3, lm4), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```

\newpage

# College dropout

All models include department fixed effects.

```{r, results='asis'}
df_temp <-
  df_grades %>%
  mutate(
    miss_age = if_else(is.na(age), 1L, 0L),
    age = if_else(is.na(age), 0, age),
  ) %>%
  group_by(stdid, e_dropped_out, reservation_stu, female, father_college, mother_college, age, miss_age, department_id) %>% 
  summarise(
    reservation_fac = mean(reservation_fac, na.rm = T),
    fac_associate_professor = mean(fac_associate_professor, na.rm = T),
    fac_professor = mean(fac_professor, na.rm = T),
    fac_yearsinhighed = mean(fac_yearsinhighed, na.rm = T),
    fac_highest_degree_phd = mean(fac_highest_degree_phd, na.rm = T),
    fac_highest_degree_phd_in_prog = mean(fac_highest_degree_phd_in_prog, na.rm = T),
    fac_degree_college_elite = mean(fac_degree_college_elite, na.rm = T),
    fac_female = mean(fac_female, na.rm = T),
  ) %>% 
  ungroup()

lm1 <-
  df_temp %>%
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_dropped_out ~ reservation_fac, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm2 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_dropped_out ~ reservation_fac + female + age + miss_age + father_college + mother_college, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm3 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_dropped_out ~ reservation_fac + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

lm4 <-
  df_temp %>% 
  drop_na(female, father_college, mother_college) %>%
  lm_robust(e_dropped_out ~ reservation_fac * reservation_stu + female + age + miss_age + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., se_type = "stata", fixed_effects = ~ department_id)

knitreg(list(lm1, lm2, lm3, lm4), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = T, booktabs = T, float.pos = "H", caption = "", digits = 2, include.nclust = F, include.rsquared = F, include.adjrs = F, include.rmse = F, omit.coef = "(miss_age)|(Intercept)")
```


\newpage

# Faculty and Student Characteristics, Faculty Differences, and Balance Checks [Updated]

```{=latex}
\begin{table}[H]
  \centering
  \begin{tabular}{@{}lllllll@{}}
    \toprule
    \multicolumn{1}{c}{}  &  & \multicolumn{5}{c}{Panel A: Faculty}  \\ \cmidrule(l){3-7}
                                      &           &               &             &           &                             &             \\
    \textbf{Faculty characteristics}  & \textbf{} & \textbf{Mean} & \textbf{SD} & \textbf{} & \textbf{Res-NonRes faculty} & \textbf{SE} \\
                                      &           &               &             &           &                             &             \\
    Reservation status                &           & 0.39          & 0.49        &           & 1.000                       &             \\
    Assistant Professor               &           & 0.72          & 0.45        &           & 0.055                       & 0.061       \\
    Associate Professor               &           & 0.18          & 0.38        &           & 0.018                       & 0.043       \\
    Professor                         &           & 0.08          & 0.27        &           & -0.071                      & 0.043       \\
    Experience in years               &           & 9.96          & 6.51        &           & -1.391*                     & 0.793       \\
    Highest degree is Masters         &           & 0.51          & 0.50        &           & 0.147**                     & 0.074       \\
    Highest degree is PhD             &           & 0.32          & 0.47        &           & -0.133***                   & 0.041       \\
    Highest degree is PhD in progress &           & 0.15          & 0.36        &           & -0.023                      & 0.068       \\
    Degree college elite              &           & 0.32          & 0.47        &           & -0.109*                     & 0.063       \\
    Female                            &           & 0.33          & 0.47        &           & -0.008                      & 0.076       \\
                                      &           &               &             &           &                             &             \\ \cmidrule(l){3-7}
    &  & \multicolumn{5}{c}{Panel B: Students} \\ \cmidrule(l){3-7}
                                      &           &               &             &           &                             &             \\
    \textbf{Student characteristics}  & \textbf{} & \textbf{Mean} & \textbf{SD} & \textbf{} & \textbf{Res-NonRes faculty} & \textbf{SE} \\
                                      &           &               &             &           &                             &             \\
    Reservation status                &           & 0.54          & 0.50        &           & -0.008                      & 0.010       \\
    Female                            &           & 0.44          & 0.50        &           & -0.002                      & 0.007       \\
    Age                               &           & 17.72         & 0.80        &           & 0.001                       & 0.011       \\
    Father college                    &           & 0.50          & 0.50        &           & 0.005                       & 0.010       \\
    Mother college                    &           & 0.35          & 0.48        &           & 0.018**                     & 0.008       \\ 
    Baseline Math score               &           & 11.64         & 4.18        &           & 0.005                       & 0.103       \\
    Baseline Physics score            &           & 9.95          & 3.97        &           & -0.039                      & 0.103       \\
    JEE Main score                    &           & 68.14         & 44.33       &           & 0.971                       & 0.920       \\
    Took JEE Main                     &           & 0.67          & 0.47        &           & 0.004                       & 0.008       \\ \bottomrule
  \end{tabular}
\end{table}
```
